---
title: "HW6"
output:
  html_document: default
  pdf_document: default
date: '2022-05-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Preparing packages and data.

```{r}
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(visdat)
library(janitor)
set.seed(45)
```

```{r}
pokemon <- read.csv('data/pokemon.csv')
head(pokemon)
```

## Exercise 1

```{r}
pokemon <- clean_names(pokemon)
pokemon <- filter(pokemon, type_1 %in% c('Bug', 'Fire', 'Grass', 'Normal', 'Water', 'Psychic'))
pokemon$type_1 = factor(pokemon$type_1)
pokemon$legendary = factor(pokemon$legendary)
pokemon$generation <- factor(pokemon$generation)
```

```{r}
pokemon_split <- initial_split(pokemon, prop = 0.8,
                                strata = type_1)
pokemon_train <- training(pokemon_split)
pokemon_test <- testing(pokemon_split)

cv_folds <- vfold_cv(pokemon_train, v = 5, strata = type_1)
```

```{r}
pokemon_recipe = recipe(type_1 ~ legendary + generation + sp_atk, + attack + speed + defense + hp + sp_def, 
                        data = pokemon_train) %>%
  step_dummy(legendary) %>%
  step_dummy(generation) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
```

## Exercise 2

```{r}
library(corrplot)
```

```{r}
M = cor(select_if(pokemon_train, is.numeric))
corrplot(M, method = 'color')
```

According to the plot, it seems like most of the variables have positive correlation with each other and especially 'total' has strong positive relationship with other variables. I think this is becasue a strong pokemon would have stronger attack and higher damage resistance. Also, 'sp_atk' and 'sp_def' variables indicate a pokemon's attack damage and damage resistance during special attacks so they have high positive correlation with 'attack' and 'defense' variables.

According to the plot, it seems like most of the variables have positive correlation with each other and espaecially 'total' has strong positive relationship with other variables. I think this is becasue a strong pokemon would have stronger attack and higher damage resistance. Also, 'sp_atk' and 'sp_def' variables indicate a pokemon's attack damage and damage resistance during special attacks so they have high positive correlation with 'attack' and 'defense' variables.

Here, I made a plot with all the numerical variables for convenience, but I variable 'x' is

## Exercise 3

```{r}
class_tree_spec <- decision_tree(cost_complexity = tune()) %>%
        set_engine("rpart") %>%
        set_mode("classification")
```

```{r}
class_tree_wf = workflow() %>%
        add_model(class_tree_spec) %>%
        add_recipe(pokemon_recipe)

pokemon_grid <- grid_regular(cost_complexity(range = c(-3, -1)), levels = 10)

tune_res <- tune_grid(
        class_tree_wf, 
        resamples = cv_folds, 
        grid = pokemon_grid, 
        metrics = metric_set(roc_auc))
```

```{r}
autoplot(tune_res)
```

## Exercise 4

```{r}
collect_metrics(tune_res) %>% arrange(mean)
```

0.6398 is the best-performing pruned decision tree on the folds.

## Exercise 5

```{r}
library(rpart.plot)
```

```{r}
best_complexity <- select_best(tune_res, metric = 'roc_auc')
pokemon_tree_final <- finalize_workflow(class_tree_wf, best_complexity)
class_tree_final_fit <- fit(pokemon_tree_final, data = pokemon_train)

class_tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot(roundint = FALSE)
```

## Exercise 5

```{r}
library(ranger)
library(randomForest)
pokemon_rf <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>% 
  set_engine('ranger', importance = 'impurity') %>%
  set_mode('classification')

pokemon_rf_wf <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(pokemon_rf)
```

```{r}
grid_rf <- grid_regular(mtry(range = c(1, 8)),
                              trees(range = c(1,10)),
                              min_n(range = c(1,10)),
                              levels = 8)

```


## Exercise 6

```{r, message = FALSE}
library(randomForest)
tune_res_rf <- tune_grid(
  pokemon_rf_wf, 
  resamples = cv_folds, 
  grid = grid_rf, 
  metrics = metric_set(roc_auc))
```

```{r}
autoplot(tune_res_rf)
```


## Exercise 7

```{r}
collect_metrics(tune_res_rf) %>% arrange(desc(mean))

collect_metrics(tune_res_rf) %>% arrange(mean)

best_parameter <- select_best(tune_res_rf, metric = "roc_auc")
```

## Exercise 8

```{r}
library(vip)
best_parameter <- select_best(tune_res_rf, metric = "roc_auc")

pokemon_rf_final <- finalize_workflow(pokemon_rf_wf, best_parameter)
pokemon_rf_final_fit <- fit(pokemon_rf_final, data = pokemon_train)
 
pokemon_rf_final_fit %>% 
  extract_fit_engine() %>% 
  vip()
```


## Exercise 9

```{r}
library(xgboost)
boost_spec <- boost_tree(trees = tune()) %>%
  set_engine('xgboost') %>%
  set_mode('classification')

boost_wf <- workflow() %>%
  add_recipe(pokemon_recipe) %>%
  add_model(boost_spec)

boost_grid <- grid_regular(trees(range = c(10, 2000)), levels = 10)

tune_boost <- tune_grid(
  boost_wf, 
  resamples = cv_folds, 
  grid = boost_grid,
  metrics = metric_set(roc_auc))

autoplot(tune_boost)
```

```{r}
collect_metrics(tune_boost) %>% arrange(desc(mean))
```


## Exercise 10

```{r}

```

## Exercise 11

```{r}

```
